A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
proofreading sec1

2D Packing Problem is defined as follows: Given a collection of rectangles $\{R_1,R_2,R_3,\dots,R_n\}$ each with a size of $w_i\times h_i, 1\leq i\leq n$, and a bin with fixed width and infinite height, we wish to pack all the rectangles into the bin without overlapping while minimizing the total bin height\cite{baker1980orthogonal}. Without loss of generality, we can normalize bin width to be 1.\par

@@

This problem is very important in many fields. In the transportation industry, this algorithm can be used to pack items into containers. There is also an interesting application of this problem in main memory allocation for multi-processor programming. Basically, this problem can be adapted to most resource allocation problems with two dimension resource constraints.\par
While the description of this problem is rather simple, there is a hidden computation complexity behind this problem. Actually, this problem is NP-Complete\cite{hartmanis1982computers}, which means that there is currently no efficient deterministic algorithm to solve it. It is easy to notice that this problem is a generalized version of the one-dimension bin packing problem\cite{johnson1974worst}. Simply restrict all the rectangles' height to be 1, this problem becomes a one-dimensional bin packing problem. We can reduce the one-dimensional bin packing problem to this problem using the idea above. Because the one-dimensional bin packing problem is NP-Hard, this problem is also NP-Hard. The optimized solution to the 2D Packing problem can be easily verified, therefore the 2D Packing Problem is also in NP. Then 2D Packing Problem is NP-Complete. With $P$ $vs$ $NP$ being an open problem, we can not find an efficient algorithm for 2D Packing Problem. \par

@@

We already show that 2D Packing Problem is NP-Complete, and P vs NP remains an open problem, so we can not find an efficient algorithm to deterministically solve it. We must try another approach. To solve an inherently difficult problem, various approaches have been well-studied. For decision problems, we can use randomized algorithms to give the correct result with high probability. For optimization problems, we can use another approach: Approximation algorithm\cite{garey1976approximation} which is guaranteed to produce a sub-optimal but reasonable result. \par

>>>>

2D Packing Problem is defined as follows: given a collection of rectangles $\{R_1,R_2,R_3,\dots,R_n\}$ each with a size of $w_i\times h_i, 1\leq i\leq n$, and a bin with fixed width and infinite height, we wish to pack all the rectangles into the bin without overlapping while minimizing the total bin height\cite{baker1980orthogonal}. Without loss of generality, we can normalize bin width to 1.\par

@@

The problem plays an important role in many fields. An algorithm for packing can be used to pack items into containers in transportation industry. There is also an interesting application of this problem in main memory allocation for multi-processor programming. Basically, this problem can be adapted to most resource allocation problems with two dimension resource constraints.
\par While the description of this problem is rather simple, there is a hidden computation complexity behind this problem. Actually, this problem is NP-Complete\cite{hartmanis1982computers}, which means that there is currently no efficient deterministic algorithm to solve it. It is easy to notice that this problem is a generalized version of the one-dimension bin packing problem\cite{johnson1974worst}. By restricting the height of all rectangles to be 1, this problem degenerates to one-dimensional bin packing problem. We can reduce the one-dimensional bin packing problem to this problem using the idea above. Because the one-dimensional bin packing problem is NP-Hard, this problem is also NP-Hard. The optimized solution to the 2D Packing problem can be easily verified, therefore the 2D Packing Problem is also in NP. Then 2D Packing Problem is NP-Complete. With $P$ $vs$ $NP$ being an open problem, we can not find an efficient algorithm for 2D Packing Problem. \par

@@

We already show that 2D Packing Problem is NP-Complete, and P vs NP remains an open problem, for which we probably cannot find an efficient algorithm to solve it deterministically. We must try another approach. To solve an inherently difficult problem, various approaches have been well-studied. For decision problems, we can use randomized algorithms to give the correct result with high probability. For optimization problems, we can use another approach: Approximation algorithm\cite{garey1976approximation} which is guaranteed to produce a sub-optimal but reasonable result. \par
